A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-14 tex/codatadp.tex
prepared table

@@

   w/o (co)data        800           1122                699
   w codata            815 (2)       1139 (3)
   w data                            1153 (6)            712 (4)
   w both                            1170 (3+6)
\end{verbatim}}

>>>>

\newcommand\landg{L\,\&\,G}
\newcommand\HD[1]{\hbox to2.5em{\hfill#1\hfill}}

\begin{table}[t!]
\begin{center}\begin{tabular}{@{}l@{\kern1em}c@{\kern.5em}c@{\kern.5em}c@{\kern1em}c@{}}
  & \HD{Distro} & \HD{\emph{AFP}} & \HD{\landg} & \HD{All}
\\[1pt] %%% TYPESETTING HACK
\midrule
%$\enatT$
\\[-9pt] %%% TYPESETTING HACK
No decision procedure
  & 800 & 922 \\
Codatatypes without bisimilarity
  &  & 936 \\
Codatatypes with bisimilarity
  &  & 939 \\
Datatypes without cyclicity
  & 815 & 947 \\
Datatypes with cyclicity
  & 815 & 953 \\
Full decision procedure
  &  & 970 \\[\jot]
Total number of goals
  & 1011\phantom{0} & 1121\phantom{0} & 899 & 3001\phantom{0}
\end{tabular}\end{center}
\caption{Number of solved goals for three benchmark suites}
\end{table}

Do we lose any problems by enabling it?

@@

   w/o (co)data        800           922                699
   w codata            815 (2)       939 (3)
   w data                            953 (6)            712 (4)
   w both                            970 (3+6)
\end{verbatim}}
